PAGAI : a path sensitive static analyser

### 2012-05-22 papers/TAPAS2012/pagai.tex
tassage
un peu de future work ?

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that \emph{Guided Static Analysis} and
\emph{Path-focusing} are sometimes faster than the classical
algorithm.
This seems due to the fact that these algorithms start on a small subset
of the graph, and then may need fewer iterations on the complete graph.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

@@

\section{Conclusion and future work}

>>>>

Table \ref{tab:time} gives the execution time of the different analysis
techniques. It is interesting to see that
\emph{Path-focusing} is sometimes faster than the classical
algorithm.
This seems due to the fact that these algorithms start on a small subset
of the graph, and then may need fewer iterations on the complete graph.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

@@

It is not totally relevant to compare by inclusion the abstract values obtained
by the various analysis techniques. Indeed, a slightly smaller invariant may not
always be useful to prove the desired properties.
A future work is thus to experiment with
better comparison metrics, such as:
\begin{itemize}
	\item the number of \emph{assert} that have been proved in the code.
		Unfortunately, it is difficult to find good benchmarks or real life
		programs with many \emph{assert} statements.
	\item the number of false alarms in a client analysis that detects array
		bound violations, arithmetic overflows, etc.
\end{itemize}
